Empowering the use of community driven preprints in ecology and evolution

### 2024-04-13 ms/ms.qmd
Fix to fig 1

# Load packages
#install.packages("pacman")
pacman::p_load(tidyverse, here, patchwork, readxl, MASS, googlesheets4, janitor, maps, forcats,RColorBrewer, flextable, ggrepel, ggimage, gt, performance, genderdata, gender, ggthemes, mapproj, DemografixeR, countrycode, see, glmmTMB, cowplot, viridis)

@@

# Plot the data
p6 <- data4 %>% filter(!is.na(gender))  %>% tabyl(gender)  %>% mutate(perc = n/sum(n)*100, labels = paste0(round(perc, 1), "%"))  %>%  ggplot(aes(x = "", y = percent, fill = gender)) +
    geom_col(color = "black") +
    geom_label_repel(aes(label = labels),
              position = position_stack(vjust = 0.6),
            show.legend = FALSE) +
    scale_fill_viridis_d() +
    coord_polar(theta = "y") + 
    theme_void() + labs(fill = "Article Type") + theme(plot.tag = element_text(size = 16, face = "bold"), plot.tag.location = "margin")

## Final plot. World map in the middle with others around

layout <- "
##AA##
BBBBBB
BBBBBB
BBBBBB
CCCDDD
CCCDDD 
"

p_summary <- p1+p2+p3+p4 + plot_layout(design = layout)+ plot_annotation(tag_levels = 'A', tag_suffix=")")
ggsave(p_summary, filename = here("output", "figs", "summary.png"), width = 10.6, height = 9.7)

>>>>

# Load packages
#install.packages("pacman")
pacman::p_load(tidyverse, here, patchwork, readxl, MASS, googlesheets4, janitor, maps, forcats,RColorBrewer, flextable, ggrepel, ggimage, gt, performance, genderdata, gender, ggthemes, mapproj, DemografixeR, countrycode, see, glmmTMB, cowplot, viridis, cowplot)

@@

# Plot the data
p6 <- data4 %>% filter(!is.na(gender))  %>% tabyl(gender)  %>% mutate(perc = n/sum(n)*100, labels = paste0(round(perc, 1), "%"))  %>%  ggplot(aes(x = "", y = percent, fill = gender)) +
    geom_col(color = "black") +
    geom_label_repel(aes(label = labels),
              position = position_stack(vjust = 0.6),
            show.legend = FALSE) +
    coord_polar(theta = "y") + 
    theme_void() + labs(fill = "Gender") + theme(plot.tag = element_text(size = 16, face = "bold"), plot.tag.location = "margin")

p7  <- ggdraw() + draw_plot(p5) + draw_plot(p6, x = 0.05, y = 0.40, width = 0.6, height = 0.6)
## Final plot. World map in the middle with others around

layout <- "
##AAAA##
BBBBBBBB
BBBBBBBB
BBBBBBBB
CCCCDDDD
CCCCDDDD
##EEEE##
##EEEE##
"

p_summary <- p1+p2+p3+p4+p7 + plot_layout(design = layout)+ plot_annotation(tag_levels = 'A', tag_suffix=")") + theme(plot.tag = element_text(size = 16, face = "bold"))
ggsave(p_summary, filename = here("output", "figs", "summary.png"), width = 11, height = 12)
